A Vignetted View of Computer Science through Citation Analysis

### 2019-12-20 Scientometrics/comp.tex
minor edits

Other classification systems are available, such as the All Science Journal Classification (ASJC) developed and maintained by Scopus, the Web of Science research and categorical classifications from Clarivate Analytics, and the National Science Foundation classification system~\cite{nsf_classification,scopus_ref,wos_ref}. Scopus and the Web of Science also include comprehensive bibliographies with citation links and proprietary unique identifiers for publications. The Scopus All Science Journal Classification (ASJC), which we use in this study is organized under into 4 subject areas, 27 major subject areas, and 334 minor subject areas. All three systems rely on applying one or more journal-derived labels to articles.  
A logical prediction, given the diversity of articles within journals, is limited specificity at the article level. 
Shu and colleagues recently noted in a comparative study of the Chinese Science Citation Database (CSCD)  and the Web of Science that 46\% of articles did not belong to the discipline of the journal they were published in~\cite{shu_comparing_2019}. 
Others have also discussed and critiqued disciplinary assignments using journal-based classifications~\cite{wang_large-scale_2016,perianes-rodriguez_comparison_2017}. 
Article classification systems have been constructed that escape some of the criticisms of journal-based classification~\cite{traag_louvain_2019,boyack_classification_2014,waltman_new_2012}, but do not seem to presently enjoy widespread use.

@@

 \emph{Overview} For the purpose of this study, our working definition of the computer science literature was all publications in the DBLP bibliography that (i) had a digital object identifier (DOI), and (ii) could also be matched to article identifiers in the Scopus bibliography. The underlying assumption is that records in DBLP are greatly enriched for computer science even while recognizing that coverage may be incomplete and possibly biased. Cross-matching DBLP publications to records in the Scopus abstract and citation database of peer-reviewed literature, enabled us to harvest the richer links in Scopus as well as extract links to publications from other disciplines. This cross-matching to Scopus also allows the use of both journal and article based classifications when clustering documents. Using both direct citations and co-citations as the basis for clustering, we used DBLP articles from journals and conference proceedings. We reconciled these clusters with the All Science Journal Classification (ASJC) developed and maintained by Scopus through a combination of automated and manual procedures, producing a dataset of  2,685,356 publications.

\emph{Data} A stable release of the DBLP computer science bibliography~\cite{dblp_ref} consisting of 7,079,994 records was downloaded as dblp-2018-08-01.xml.gz. Slightly over 95\% of the publications within were published after 1996. Publications were parsed from the XML source file and loaded into a PostgreSQL database. As part of implementing a larger data platform for research evaluation~\cite{GithubERNIE2019}, we have previously parsed the Scopus dataset, presently at over 87.8 million publications, into a custom schema in a PostgreSQL database. The total number of publications in Scopus labeled with major subject area of Computer Science (in turn a subset of the Physical Sciences subject area) is 5,835,160. Records in the DBLP dataset were matched to Scopus identifiers using digital object identifiers (DOIs). This procedure resulted in a dataset of 2,685,356 DBLP publications with Scopus identifiers where 1,278,322 (47.6\%) were labeled as article and 1,407,034 (52.4\%) as conference proceedings.  References cited by these publications were then extracted from Scopus (7,129,006 records), resulting in a total of 8,000,411 
publications and references. 
We represented these data using a graph where the 8,000,411 nodes represent
publications and references  and the 44,296,381 undirected edges represent citations within the dataset. 
We refer to these data as the  \emph{comp} dataset (Fig~\ref{fig:ar_cp_annotation}, Table~\ref{tab:comp}).

@@

 \emph {Direct Citation} Graclus~\cite{graclus_2007} is a spectral graph clustering package that optimizes  various clustering criteria, including normalized cut, ratio cut, and ratio association, that has previously been applied to citation data~\cite{subelj_clustering_2016}. 
We used v1.2 in our experiments. The \emph{comp} dataset was formatted as an undirected graph, stored in a file with a header line indicating the number of nodes and edges, and used as input to Graclus, which requires the number of clusters to be formed as an input parameter. In preliminary experiments, we varied the number of clusters to be formed between 10 and 50 clusters (data not shown).  At around 20 clusters, clusters size was relatively stable with the largest cluster containing roughly 10 times the number of nodes in the smallest one~\cite{subelj_clustering_2016}. Consequently, we used Graclus to generate 20 clusters, labeled 0-19 (Table~\ref{tab:graclus}), analogous to Level 1 of Waltman and van Eck's mapping of nearly 10 million publications but focused on the DBLP bibliography rather than a broader Web of Science sample~\cite{waltman_new_2012}.

@@

We used a modification of variable level clustering combined with agglomerative clustering, an approach developed in 1985 by Small and Sweeney~\cite{small_clustering_1985} for co-citation analysis.Variable level clustering involves applying a threshold (below which all edges in a graph are deleted) then iteratively selecting edges with the highest normalized co-citation value and extracting connected components from the graph as clusters for each edge in turn. Three parameters are needed: (i) a threshold or starting level based on a quantile of normalized co-citation frequency, (ii) a level increment, and (iii) a maximum cluster size. An issue is the generation of very large clusters by chaining via low edge weights.  Thus, at each iteration, any cluster exceeding the maximum cluster size  is returned to the process and a higher threshold is applied to break such clusters.

@@

We applied variable clustering with initial parameters as follows: the threshold  $t$  is initially set to  the median normalized co-citation frequency (quantile=0.5), increment $i = 0.1$, and maximum cluster size, $mcs=200$. Thus, at start, all edges below the median normalized co-citation frequency were deleted. Clusters were formed by assembling connected components from each co-cited pair beginning with the heaviest edge weight. Clusters below size 100 were retained and any cluster larger than 200 nodes was carried over to the next round. The threshold, $t$, was then incremented by 0.1 and the process repeated while progressively incrementing $t$.  We used a bi-phasic approach where in which $t$ ranged from 0.5--0.9, after which $i$ was reduced to 0.01 for the range $0.9 \leq t \leq 0.99$. A final threshold of $t$=0.999 was applied to break the single remaining large cluster.  Using this approach, 22,232 clusters containing 84,591 nodes were generated, each containing less than 100 nodes. Clusters containing only 2 nodes were discarded, bringing the total number of clusters down to 10,298. The publications in these 10,298 clusters were overwhelmingly drawn from the Physical Sciences (one of the four top level categories in the Scopus ASJC classification), of which computer science is a sub-category (Fig.~\ref{fig:quad-chart}).

@@

\emph{Data} The process of selection and matching resulted in a dataset of  publications (Materials and Methods). Of 4,291,130 DBLP publications with DOIs, only  2,685,356 had corresponding DOIs in Scopus. Of these roughly 2.68 million publications, approximately 2.07 million were assigned ASJC codes in Scopus corresponding to Computer Science (major subject area with 13 minor subject areas (Table~\ref{tab:comp}), with the balance of 610,000 publications non-exclusively shared between 26 different major subject areas ranging from Engineering (330,048) to Dentistry (Fig.~\ref{fig:ar_cp_annotation}). The set of 2.07 million publications classified under the major subject area Computer Science in Scopus spanned all 13 minor subject areas with Software 30.3\% being the largest component and Computer Science (miscellaneous) 0.9\% the smallest. Publications in the \emph{comp} dataset labeled Theoretical Computer Science (409,082) are classified under the the major subject area of Mathematics rather than Computer Science (Table~\ref{tab:comp}).

@@

Figure~\ref{fig:heatmap} permits examination of these data from two perspectives: (i) rows: the clusters that map to a given ASJC minor subject area (ii) columns: ASJC minor subject areas that comprised at least 15\% of the publication in a cluster. Under these conditions of clustering and this threshold of 15\%, 31 of the 334 ASJC minor subject areas are represented. Unsurprisingly, the broad categories Computer Science Applications, Software, and Electrical and Electronic Engineering register in 16, 12, and 10 clusters respectively, while Artificial Intelligence mapped to 7 different clusters. At the other end of the range, 12 of the 31 ASJC minor subject areas were each detected in a single cluster.

From the alternate perspective (columns), Cluster 17 was the most diverse and contained publications annotated with 8 minor subject area labels: Biochemistry, Chemistry(all), Genetics, Molecular Biology,  Statistics \& Probability, Computational Theory \& Mathematics, and Computational Mathematics. Cluster 19 mapped to two areas but was excluded from qualitative analysis because of its high conductance value. Of the remaining clusters, Cluster 2 represents interactions between the minor subject areas Theoretical Computer Science, Discrete Mathematics and Combinatorics, and Applied Mathematics as well as the more generic Computer Science (all). Clusters 3 and 4 include Computer Networks and Communications, and Cluster 18 (Artificial Intelligence, Cognitive Neuroscience, and Neurology) and clusters 5--9 include Management Science, Operations Research, Information Systems, Modeling and Simulation, and Human-Computer Interaction.

These data suggest that areas central to computer science in 2019 (Salton and Bergmark's historical triad of hardware, software, and theory) are more likely to be found in multiple clusters than peripheral topics. A second inference is that, in some cases, journal-based classification and our article clusters align fairly well (Hardware and Architecture). 
A third inference is that the ASJC minor subject area ``Computer Applications" is relatively broad, and publications thus labeled are present at the $>=$ 15\% level in 16 out of 20 clusters).  Finally,   for this DBLP dataset, as we clustered it, interactions with fields outside computer science such as Biology are (Biochemistry, Neurology)  are  detected in two separate clusters. The first appears to be the interaction of Biochemistry, Molecular Biology, and Genetics with Statistics, Mathematics, and Computer Science. The second is the interaction of Neurology, Cognitive Neuroscience, and Artificial Intelligence.

@@

At the threshold of 15\%, only 17 of 20 co-citation clusters mapped to at least one minor subject areas. In contrast to a maximum of eight minor subject areas for clustering by direct citation at the 15\% threshold (Fig. 3, Cluster 17), no co-citation cluster maps to more than three minor subject areas. The threshold had to be reduced to 10\%, for all 20 co-citation clusters to map to at least one minor subject area. We interpret these data as indicative of broader clusters created by weaker linkages that accumulate during the agglomerative clustering phase~\cite{small_clustering_1985}.

Clustering by co-citation begins, for each cluster, with a pair of nodes that nucleates its subsequent formation. Thus, we also designated the pair of nodes in a cluster with the strongest edge as its nucleating cluster and labeled the cluster by inspecting this pair of documents and assigning an intuitive label to it. These labels are compared to the minor subject area that accounts for the largest fraction of the nodes in a co-citation cluster (Table~\ref{tab:centroid_reconcile}). The extent of correspondence between the manually applied label and the ASJC minor subject area suggest that using the nucleating cluster as the basis for labeling co-citation clusters (as we generated them) may be valid although its usefulness is likely to vary according to the data being examined. We provide the DOIs of these nucleating pairs matched to manually assigned labels for independent review (Table~\ref{tab:centroid}.

To examine the correspondence between clusters generated by direct citation vs co-citation, we mapped the contents of these clusters to each other, Fig~\ref{fig:graclus_cocit_fig}. At a threshold of 15\%, similar to other cross-matching, 90\% (18/20) of the co-cited clusters mapped to 1 or 2 direct citation clusters. This suggests that the majority of co-cited pairs tend to lie within the same cluster of publications linked by citations and by extension, tend towards disciplinarity rather then interdisciplinarity.

\section{Discussion} Considering expansion and diversification of the field of computer science, we revisited its characterization in 1979~\cite{salton_citation_1979} . In comparison to Salton and Bergmark, we analyzed considerably more data, 2.68 million publications versus 391 by using two bibliographic databases, DBLP and Scopus, consisting of  7.1 million and 87.8 million publications respectively. By linking the two datasets to harvest citation and metadata, we were able to construct article level clusters in two different ways and reconcile these clusters with the Scopus ASJC classification, which provides a journal level perspective.

Reconciling direct citation clusters to the Scopus ASJC classification yielded partially overlapping results that are consistent with the observation of Waltman and van Eck (2012)~\cite{waltman_new_2012}, `that traditional disciplines such as those just mentioned only partly reflect the actual organization of today’s scientific research'. Of interest to us, was the single obviously multidisciplinary cluster in which at least 15\% of its component publications were labeled with the ASJC minor subject areas Biochemistry, Chemistry, Computational Mathematics, Computational Theory and Mathematics, Computer Science Applications, Genetics, Molecular Biology, Statistics \& Probability. A second cluster mapped to Artificial Intelligence, Cognitive Neuroscience, and Neurology.  Both suggest collaboration between computer science and biology. At the opposite end of this spectrum is the, perhaps more insular, cluster that maps to Hardware and Architecture, Electrical and Electronic Engineering, and Software. These data suggest that, at least from the perspective of a high level of aggregation, some subfields within computer science may be primarily inward looking (remain concerned with fundamental questions in computer science and electrical engineering), while others are more actively engaged with fields external to computer science.

@@

Reasonable critiques of our approach are: (i) use of the DBLP dataset and the efficiency of matching to Scopus, which may not capture all aspects of computer science and its interactions with other fields, (ii) the basis for clustering and (iii) mapping the results of this clustering against a classification designed around journals rather than individual articles. Our focus on high-level features and a preference for simplicity and intuitiveness in our choice of methods may mitigate these concerns.

>>>>

Other classification systems are available, such as the All Science Journal Classification (ASJC) developed and maintained by Scopus, the Web of Science research and categorical classifications from Clarivate Analytics, and the National Science Foundation classification system~\cite{nsf_classification,scopus_ref,wos_ref}. Scopus and the Web of Science also include comprehensive bibliographies with citation links and proprietary unique identifiers for publications. The Scopus All Science Journal Classification (ASJC), which we use in this study, is organized  into 4 subject areas, 27 major subject areas, and 334 minor subject areas. All three systems rely on applying one or more journal-derived labels to articles.  
A logical prediction, given the diversity of articles within journals, is limited specificity at the article level. 
Shu and colleagues recently noted in a comparative study of the Chinese Science Citation Database (CSCD)  and the Web of Science that 46\% of articles did not belong to the discipline of the journal they were published in~\cite{shu_comparing_2019}. 
Others have also discussed and critiqued disciplinary assignments using journal-based classifications~\cite{wang_large-scale_2016,perianes-rodriguez_comparison_2017}. 
Article classification systems have been constructed that escape some of the criticisms of journal-based classification~\cite{traag_louvain_2019,boyack_classification_2014,waltman_new_2012}, but do not seem to presently enjoy widespread use.

@@

 \emph{Overview} For the purpose of this study, our working definition of the computer science literature is all publications in the DBLP bibliography that (i) had a digital object identifier (DOI), and (ii) could also be matched to article identifiers in the Scopus bibliography. The underlying assumption is that records in DBLP are greatly enriched for computer science even while recognizing that coverage may be incomplete and possibly biased. Cross-matching DBLP publications to records in the Scopus abstract and citation database of peer-reviewed literature enabled us to harvest the richer links in Scopus as well as extract links to publications from other disciplines. This cross-matching to Scopus also allows the use of both journal and article based classifications when clustering documents. Using both direct citations and co-citations as the basis for clustering, we used DBLP articles from journals and conference proceedings. We reconciled these clusters with the All Science Journal Classification (ASJC) developed and maintained by Scopus through a combination of automated and manual procedures, producing a dataset of  2,685,356 publications.

\emph{Data} A stable release of the DBLP computer science bibliography~\cite{dblp_ref} consisting of 7,079,994 records was downloaded as dblp-2018-08-01.xml.gz. 
Slightly over 95\% of the publications within were published after 1996. 
Publications were parsed from the XML source file and loaded into a PostgreSQL database. As part of implementing a larger data platform for research evaluation~\cite{GithubERNIE2019}, we have previously parsed the Scopus dataset, presently at over 87.8 million publications, into a custom schema in a PostgreSQL database. 
The total number of publications in Scopus labeled with major subject area Computer Science (in turn a subset of the Physical Sciences subject area) is 5,835,160. Records in the DBLP dataset were matched to Scopus identifiers using digital object identifiers (DOIs). This procedure resulted in a dataset of 2,685,356 DBLP publications with Scopus identifiers where 1,278,322 (47.6\%) were labeled as article and 1,407,034 (52.4\%) as conference proceedings.  References cited by these publications were then extracted from Scopus (7,129,006 records), resulting in a total of 8,000,411 
publications and references. 
We represented these data using a graph where the 8,000,411 nodes represent
publications and references  and the 44,296,381 undirected edges represent citations within the dataset. 
We refer to these data as the  \emph{comp} dataset (Fig~\ref{fig:ar_cp_annotation}, Table~\ref{tab:comp}).

@@

 \emph {Direct Citation} Graclus~\cite{graclus_2007} is a spectral graph clustering package that optimizes  various clustering criteria, including normalized cut, ratio cut, and ratio association, and that has previously been applied to citation data~\cite{subelj_clustering_2016}. 
We used v1.2 in our experiments. The \emph{comp} dataset was formatted as an undirected graph, stored in a file with a header line indicating the number of nodes and edges, and used as input to Graclus, which requires the number of clusters to be formed as an input parameter. In preliminary experiments, we varied the number of clusters to be formed between 10 and 50 clusters (data not shown).  At around 20 clusters, clusters size was relatively stable with the largest cluster containing roughly 10 times the number of nodes in the smallest one~\cite{subelj_clustering_2016}. Consequently, we used Graclus to generate 20 clusters, labeled 0-19 (Table~\ref{tab:graclus}), analogous to Level 1 of Waltman and van Eck's mapping of nearly 10 million publications but focused on the DBLP bibliography rather than a broader Web of Science sample~\cite{waltman_new_2012}.

@@

We used a modification of variable level clustering combined with agglomerative clustering, an approach developed in 1985 by Small and Sweeney~\cite{small_clustering_1985} for co-citation analysis.
Variable level clustering involves applying a threshold (below which all edges in a graph are deleted) then iteratively selecting edges with the highest normalized co-citation value and extracting connected components from the graph as clusters for each edge in turn. Three parameters are needed: (i) a threshold or starting level based on a quantile of normalized co-citation frequency, (ii) a level increment, and (iii) a maximum cluster size. An issue is the generation of very large clusters by chaining via low edge weights.  Thus, at each iteration, any cluster exceeding the maximum cluster size  is returned to the process and a higher threshold is applied to break such clusters.

@@

We applied variable clustering with initial parameters as follows: the threshold  $t$  is initially set to  the median normalized co-citation frequency (quantile=0.5), increment $i = 0.1$, and maximum cluster size, $mcs=200$. Thus, at the start, all edges below the median normalized co-citation frequency were deleted. Clusters were formed by assembling connected components from each co-cited pair beginning with the heaviest edge weight. Clusters below size 100 were retained and any cluster larger than 200 nodes was carried over to the next round. The threshold, $t$, was then incremented by 0.1 and the process repeated while progressively incrementing $t$.  We used a bi-phasic approach where in which $t$ ranged from 0.5--0.9, after which $i$ was reduced to 0.01 for the range $0.9 \leq t \leq 0.99$. A final threshold of $t$=0.999 was applied to break the single remaining large cluster.  Using this approach, 22,232 clusters containing 84,591 nodes were generated, each containing less than 100 nodes. Clusters containing only two nodes were discarded, bringing the total number of clusters down to 10,298. The publications in these 10,298 clusters were overwhelmingly drawn from the Physical Sciences (one of the four top level categories in the Scopus ASJC classification), of which computer science is a sub-category (Fig.~\ref{fig:quad-chart}).

@@

\emph{Data} The process of selection and matching resulted in a dataset of  publications (Materials and Methods). Of 4,291,130 DBLP publications with DOIs, only  2,685,356 had corresponding DOIs in Scopus. Of these roughly 2.68 million publications, approximately 2.07 million were assigned ASJC codes in Scopus corresponding to Computer Science (major subject area with 13 minor subject areas (Table~\ref{tab:comp}), with the balance of 610,000 publications non-exclusively shared between 26 different major subject areas ranging from Engineering (330,048) to Dentistry (Fig.~\ref{fig:ar_cp_annotation}). The set of 2.07 million publications classified under the major subject area Computer Science in Scopus spanned all 13 minor subject areas with Software at 30.3\%  being the largest component and Computer Science (miscellaneous) at 0.9\% the smallest. Publications in the \emph{comp} dataset labeled Theoretical Computer Science (409,082) are classified under the the major subject area of Mathematics rather than Computer Science (Table~\ref{tab:comp}).

@@

Figure~\ref{fig:heatmap} permits examination of these data from two perspectives: (i) rows: the clusters that map to a given ASJC minor subject area and (ii) columns: ASJC minor subject areas that comprised at least 15\% of the publication in a cluster. Under these conditions of clustering and this threshold of 15\%, 31 of the 334 ASJC minor subject areas are represented. Unsurprisingly, the broad categories Computer Science Applications, Software, and Electrical and Electronic Engineering register in 16, 12, and 10 clusters respectively, while Artificial Intelligence mapped to 7 different clusters. At the other end of the range, 12 of the 31 ASJC minor subject areas were each detected in a single cluster.

From the alternate perspective (columns), Cluster 17 was the most diverse and contained publications annotated with 8 minor subject area labels: Biochemistry, Chemistry(all), Genetics, Molecular Biology,  Statistics \& Probability, Computational Theory \& Mathematics, and Computational Mathematics. Cluster 19 mapped to two areas but was excluded from qualitative analysis because of its high conductance value. 
Of the remaining clusters, Cluster 2 represents interactions between the four minor subject areas Theoretical Computer Science, Discrete Mathematics and Combinatorics, Applied Mathematics,  and the more generic Computer Science (all). Clusters 3 and 4 include Computer Networks and Communications, and Cluster 18 (Artificial Intelligence, Cognitive Neuroscience, and Neurology) and clusters 5--9 include Management Science, Operations Research, Information Systems, Modeling and Simulation, and Human-Computer Interaction.

These data suggest that areas central to computer science in 2019 (Salton and Bergmark's historical triad of hardware, software, and theory) are more likely to be found in multiple clusters than peripheral topics. A second inference is that, in some cases, journal-based classification and our article clusters align fairly well (Hardware and Architecture). 
A third inference is that the ASJC minor subject area ``Computer Applications" is relatively broad, and publications thus labeled are present at the $>=$ 15\% level in 16 out of 20 clusters.  Finally,   for this DBLP dataset, as we clustered it, interactions with fields outside computer science such as Biology are (Biochemistry, Neurology)  are  detected in two separate clusters. The first appears to be the interaction of Biochemistry, Molecular Biology, and Genetics with Statistics, Mathematics, and Computer Science, and the second is the interaction of Neurology, Cognitive Neuroscience, and Artificial Intelligence.

@@

At the threshold of 15\%, only 17 of 20 co-citation clusters mapped to at least one minor subject areas. In contrast to a maximum of eight minor subject areas for clustering by direct citation at the 15\% threshold (Fig. 3, Cluster 17), no co-citation cluster maps to more than three minor subject areas. The threshold had to be reduced to 10\% for all 20 co-citation clusters to map to at least one minor subject area. We interpret these data as indicative of broader clusters created by weaker linkages that accumulate during the agglomerative clustering phase~\cite{small_clustering_1985}.

Clustering by co-citation begins, for each cluster, with a pair of nodes that nucleates its subsequent formation. Thus, we also designated the pair of nodes in a cluster with the strongest edge as its nucleating pair and labeled the cluster by inspecting this pair of documents and assigning an intuitive label to it. These labels show high degree of correspondence  to the ASJC minor subject area that accounts for the largest fraction of the nodes in a co-citation cluster (Table~\ref{tab:centroid_reconcile}). 
The extent of this correspondence %between the manually applied label and the ASJC minor subject area 
suggests that using the nucleating cluster as the basis for labeling co-citation clusters (as we generated them) may be valid, although its usefulness is likely to vary according to the data being examined. We provide the DOIs of these nucleating pairs matched to manually assigned labels for independent review (Table~\ref{tab:centroid}.

To examine the correspondence between clusters generated by direct citation vs co-citation, we mapped the contents of these clusters to each other (Fig~\ref{fig:graclus_cocit_fig}).
 At a threshold of 15\%, similar to other cross-matching, 90\% (18/20) of the co-cited clusters mapped to 1 or 2 direct citation clusters. This suggests that the majority of co-cited pairs tend to lie within the same cluster of publications linked by citations and,  by extension, tend towards disciplinarity rather than interdisciplinarity.

\section{Discussion} Considering expansion and diversification of the field of computer science, we revisited its characterization in 1979~\cite{salton_citation_1979}. In comparison to Salton and Bergmark, we analyzed considerably more data, 2.68 million publications versus 391 by using two bibliographic databases, DBLP and Scopus, consisting of  7.1 million and 87.8 million publications respectively. By linking the two datasets to harvest citation and metadata, we were able to construct article level clusters in two different ways and reconcile these clusters with the Scopus ASJC classification, which provides a journal level perspective.

Reconciling direct citation clusters to the Scopus ASJC classification yielded partially overlapping results that are consistent with the observation of Waltman and van Eck (2012)~\cite{waltman_new_2012} `that traditional disciplines such as those just mentioned only partly reflect the actual organization of today’s scientific research'. Of interest to us was the single obviously multidisciplinary cluster in which at least 15\% of its component publications were labeled with the ASJC minor subject areas Biochemistry, Chemistry, Computational Mathematics, Computational Theory and Mathematics, Computer Science Applications, Genetics, Molecular Biology, Statistics \& Probability. A second cluster mapped to Artificial Intelligence, Cognitive Neuroscience, and Neurology.  Both suggest collaboration between computer science and biology. At the opposite end of this spectrum is the perhaps more insular cluster that maps to Hardware and Architecture, Electrical and Electronic Engineering, and Software. These data suggest that, at least from the perspective of a high level of aggregation, some subfields within computer science may be primarily inward looking (remain concerned with fundamental questions in computer science and electrical engineering), while others are more actively engaged with fields external to computer science.

@@

Reasonable critiques of our approach are: (i) use of the DBLP dataset and the efficiency of matching to Scopus, which may not capture all aspects of computer science and its interactions with other fields, (ii) the basis for clustering, and (iii) mapping the results of this clustering against a classification designed around journals rather than individual articles. Our focus on high-level features and a preference for simplicity and intuitiveness in our choice of methods may mitigate these concerns.
